---
title: "EDA"
output: html_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(ggridges)
library(leaflet)
```


```{r}
library(p8105.datasets)

data(nyc_airbnb)
```

### Brainstorm questions

*Where are max and min air bnb prices?
  *what are average prices?
*Where are prices going up and down over time?
*What's the relationship between number of reviews and average review?
*Does room type affect availability?
*What's the location of the unit? 
  *What area are popular?
  *Popularity = number of units? Average price?
*Are there repeat hosts?
  *If so, what does that mean? 
  
```{r}
str(nyc_airbnb)
```

## *Where are max and min air bnb prices?
```{r}
mean(pull(nyc_airbnb, price))
```

```{r}
nyc_airbnb %>%
  filter(calculated_host_listings_count > 1) %>%
  distinct(host_id, host_name, calculated_host_listings_count)
```

```{r}
nyc_airbnb |>
  ggplot(aes(x = review_scores_location, y = price)) +
  geom_point()
```

```{r}
nyc_airbnb |>
  filter(neighbourhood_group == "Manhattan",
         price < 1000) |>
  ggplot(aes(x = lat, y = long, color = price)) +
  geom_point(alpha = .1)
```

```{r}
nyc_airbnb |>
   filter(neighbourhood_group == "Manhattan",
   price < 1000,
   room_type == "Entire home/apt") |>
  group_by(neighbourhood) |>
  summarize(mean_price = mean(price)) |>
  arrange(desc(mean_price))
```



```{r}
nyc_airbnb |>
  filter(
    neighbourhood_group == "Manhattan",
    price < 1000) |>
  leaflet() |>
  addTiles() |>
  addMarkers(~lat, ~long)
  
```

